\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{setspace}
\usepackage{color}
\definecolor{oucrimson}{RGB}{132,22,23}
\usepackage[colorlinks=true,
            urlcolor=oucrimson,
            linkcolor=black,
            citecolor=black]{hyperref}
\doublespacing

% --------------------------------------------------
\title{Problem Set 1}
\author{Tristan Winkle}
\date{}

% --------------------------------------------------
\begin{document}
\maketitle
% --------------------------------------------------

% --------------------------------------------------
\section{Summary}
% --------------------------------------------------

\paragraph{Interests in Economics \& Data Science}
My broad interests are in Labor and Development Economics. I am drawn to the empirical and topical breadth of these fields. Regarding data science, I am particularly interested in building and managing datasets to ready them for econometric analysis. I also deeply care about measurement and democratizing data access.

\paragraph{Motivation for this Class}
I view this course as an opportunity to build on the structural modeling skills I developed last fall. Additionally, I look forward to engaging with a cohort and professor whose research interests and methodological focus align closely with my own.

\paragraph{Project Ideas}
I have not yet converged on a specific topic, but I plan to leverage ongoing RA/co-author work. Two potential avenues include managing a large-scale peer effects panel (1M+ observations) with Dr. Carlson, or web-scraping disaster notifications from \href{https://reliefweb.int/}{ReliefWeb} for Dr. Hamory. Ideally, I would like to work through my long list of ideas and jump-start dissertation work through this course. 

\paragraph{Goals for the Class}
My primary goal is to enhance my competitiveness for the job market by expanding my methodological toolkit. Specifically, I aim to refine my data management workflows, improve research productivity, and produce high-quality, organized output. I would also like to have fun. 

\paragraph{Post-Graduation Plans}
Like many PhD candidates, I plan to apply to a diverse range of positions across government, industry, and academia. I am passionate about research and have deeply valued my time tutoring in the ELL; therefore, my ideal role is one that combines independent research with the opportunity to mentor students or junior economists.

% --------------------------------------------------
\section{Equation}
% --------------------------------------------------

\begin{equation}
	a^{2} + b^{2} = c^{2}
\end{equation}

% --------------------------------------------------
\end{document}
% --------------------------------------------------
